Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-08 text/supp.tex

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../analysis/ts-gpdd-heavy-eg-log10-base.pdf}
\caption{
  Time series for populations with Pr($\nu < 10$) $>$ 0.5 using the base
  Gompertz population model. Panels are ordered by increasing Pr($\nu < 10$).
  Vertical axes are on a log10 scale. Colours indicate taxonomic classes. The
  labels on each panel indicate Pr($\nu < 10$) $>$ 0.5, the common name for the
  species, and the Global Population Dynamics Database ID number.
}
\label{fig:heavy-ts}
\end{center}
\end{figure}

>>>>

\LTcapwidth=\textwidth
\bibpunct{}{}{;}{a}{}{;}

\singlespacing
\begin{footnotesize}
\begin{longtable}{>{\RaggedRight}m{1.5cm}>{\RaggedRight}p{4.3cm}>{\RaggedRight}p{0.8cm}>{\RaggedRight}p{1.7cm}>{\RaggedRight}p{1.0cm}>{\RaggedRight}p{3.0cm}>{\RaggedRight}p{1.7cm}>{\RaggedRight}p{0.8cm}}
\caption{Populations with Pr$(\nu < 10) > 0.5$. TODO}\\
\toprule
\input{../analysis/cause-table.tex}
\label{tab:causes-supp}
\end{longtable}
\end{footnotesize}
\onehalfspacing

@@

% \begin{figure}[htbp]
% \begin{center}
% \includegraphics[width=0.9\textwidth]{../analysis/ts-gpdd-heavy-eg-log10-base.pdf}
% \caption{
%   Time series for populations with Pr($\nu < 10$) $>$ 0.5 using the base
%   Gompertz population model. Panels are ordered by increasing Pr($\nu < 10$).
%   Vertical axes are on a log10 scale. Colours indicate taxonomic classes. The
%   labels on each panel indicate Pr($\nu < 10$) $>$ 0.5, the common name for the
%   species, and the Global Population Dynamics Database ID number.
% }
% \label{fig:heavy-ts}
% \end{center}
% \end{figure}
%
% \clearpage
